---
title:  "GSS Model"
author: "Paul Frater"
date:   ""
output: html_document
---
```{r global_options, include=F}
knitr::opts_chunk$set(fig.width=12, fig.height=8, echo=F, warning=F, message=F)
knitr::opts_knit$set(root.dir = '~/gadget/gadget-models/grSilverSmelt/gssModel')
```

# Gadget Model for greater silver smelt

```{r, gadget results, include=F}
library(plyr)
library(dplyr)
library(ggplot2)
library(grid)
library(Rgadget)
setwd('~/gadget/gadget-models/grSilverSmelt/gssModel')
fit <- gadget.fit(wgts="WGTS", main.file='WGTS/main.final',
                  fleet.predict = data.frame(fleet = 'bmt.comm', ratio=1),
                  mat.par=c(-18.2401844, 0.5536777))
```

<!-- Add specific results/figures you want presented here-->

## Likelihoood
These likelihoods are still really low for all the length and age-length distributions. I'm not quite sure how to interpret this.
```{r}
summary.plot <-
    ggplot(filter(fit$likelihoodsummary, year != 'all'),
           aes(as.numeric(year), likelihood.value)) +
    geom_point() + facet_wrap(~component) +theme_bw()+
    xlab('Year') + ylab('Score')
```

```{r}
resTable <- fit$resTable[tail(head(names(fit$resTable),-2),-1)]

## to calculate biomass index
tmp <- mutate(fit$sidat, survey = ifelse(substr(name,1,3)=='aut','aut', 'igfs'))
tmp <- rbind.fill(tmp,
                  ddply(tmp,~year+survey, summarise,
                        number.x = sum(number.x*0.000003129303*lower^3.224769 ),
                        predict = sum(predict*0.000003129303*lower^3.224769 ),
                        upper = sum(upper*0.000003129303*lower^3.224769 ),
                        lower = sum(lower*0.000003129303*lower^3.224769 ),
                        length = 'Biomass'))

```

## Survey Indices
For Spring
```{r}
# plot the model survey data over the actual survey data
si.fit.spr.survey <-
    ggplot(subset(tmp, survey=='igfs'), aes(year,number.x)) +
    geom_point() +
    geom_line(aes(year,predict)) +
    geom_linerange(data=subset(tmp,year==max(year)),
                   aes(year,ymax=number.x,ymin=predict),col='green')+
    geom_text(data=mutate(subset(tmp,year==min(year)),y=Inf),
              aes(year,y,label=length), vjust = 2,hjust = -1)+
    facet_wrap(~length,scale='free_y',ncol=2) + theme_bw() +
    ylab('Index') + xlab('Year') +
    theme (panel.margin = unit(0,'cm'), plot.margin = unit(c(0,0,0,0),'cm'),
           strip.background = element_blank(), strip.text.x = element_blank())
si.fit.spr.survey
```

and Autumn
``` {r}
si.fit.aut.survey <-
    ggplot(subset(tmp, survey=='aut'), aes(year,number.x)) +
    geom_point() +
    geom_line(aes(year,predict)) +
    geom_linerange(data=subset(tmp,year==max(year)),
                   aes(year,ymax=number.x,ymin=predict),col='green')+
    geom_text(data=mutate(subset(tmp,year==min(year)),y=Inf),
              aes(year,y,label=length), vjust = 2,hjust = -1)+
    facet_wrap(~length,scale='free_y',ncol=2) + theme_bw() +
    ylab('Index') + xlab('Year') +
    theme (panel.margin = unit(0,'cm'), plot.margin = unit(c(0,0,0,0),'cm'),
           strip.background = element_blank(), strip.text.x = element_blank())
si.fit.aut.survey
```

## Length Distributions
For Spring Surveys
```{r}
ldist.fit.spr.survey <-
    ggplot(subset(fit$catchdist.fleets,name == 'ldist.igfs') ,
           aes(lower,predicted)) + geom_line() +
    geom_line(aes(lower,observed),col='gray') +
    facet_wrap(~year+step) + theme_bw() + 
    geom_text(data=mutate(subset(fit$catchdist.fleets,
                                 name == 'ldist.igfs' & lower==min(lower)),y=Inf),
              aes(lower,y,label=year), vjust = 2,hjust = -1)+
    ylab('Proportion') + xlab('length') +
    theme (axis.text.y = element_blank(), axis.ticks.y = element_blank(),
           panel.margin = unit(0,'cm'), plot.margin = unit(c(0,0,0,0),'cm'),
           strip.background = element_blank(), strip.text.x = element_blank())
ldist.fit.spr.survey
```

And Autumn Surveys
``` {r}
ldist.fit.aut.survey <-
    ggplot(subset(fit$catchdist.fleets,name == 'ldist.aut') ,
           aes(lower,predicted)) + geom_line() +
    geom_line(aes(lower,observed),col='gray') +
    facet_wrap(~year+step) + theme_bw() + 
    geom_text(data=mutate(subset(fit$catchdist.fleets,
                                 name == 'ldist.aut' & lower==min(lower)),y=Inf),
              aes(lower,y,label=year), vjust = 2,hjust = -1)+
    ylab('Proportion') + xlab('length') +
    theme (axis.text.y = element_blank(), axis.ticks.y = element_blank(),
           panel.margin = unit(0,'cm'), plot.margin = unit(c(0,0,0,0),'cm'),
           strip.background = element_blank(), strip.text.x = element_blank())
ldist.fit.aut.survey
```

And for the catch
``` {r}
# plot the model catchdistribution data over actual catchdistribution data
ldist.fit.catch <-
    ggplot(subset(fit$catchdist.fleets,name == 'ldist.bmt'),
           aes(lower,predicted)) +
    geom_line(aes(lower,observed),col='gray') +
    facet_wrap(~year+step) + theme_bw() + geom_line() +
    geom_text(data=mutate(subset(fit$catchdist.fleets,
                                 name == 'ldist.bmt' & lower==min(lower)),y=Inf),
              aes(lower,y,label=year), vjust = 2,hjust = -1)+
    ylab('Proportion') + xlab('length') +
    theme (axis.text.y = element_blank(), axis.ticks.y = element_blank(),
           panel.margin = unit(0,'cm'), plot.margin = unit(c(0,0,0,0),'cm'),
           strip.background = element_blank(), strip.text.x = element_blank())
ldist.fit.catch
```

## Suitability
``` {r}
# plot suitability against length for both survey and commercial fleets
selection.plot <-
    ggplot(fit$suitability,
           aes(l,suit,lty=fleet, color=stock)) +
    geom_line() +
    theme_bw() + ylab('Suitability') + xlab('Length') +
    theme(legend.position = c(0.8,0.25), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm')) 
selection.plot
```

## Growth
``` {r}
# plot growth curve from model
gr.plot <-
    ggplot(fit$stock.growth,
           aes(age,length)) + 
    geom_line() +
    theme_bw() + ylab('Length') + xlab('Age') +
    theme(legend.position = c(0.9,0.75), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm'))
gr.plot
```

## Recruitment
For the immature stock
``` {r}
# plot recruitment of stock by year
rec.plot <-
    ggplot(filter(fit$res.by.year, stock=='gssimm'), aes(year,recruitment/1e6)) +
    geom_bar(stat='identity') +
    ylab("Recruitment (in millions)") + xlab('Year') +  theme_bw() +
    theme(legend.position = c(0.25,0.75), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm'))
rec.plot
```

## Landings By Year
``` {r}
# plotting the catch by year
catch.plot <- 
ggplot(fit$res.by.year,aes(year,catch/1000)) +
    geom_bar(stat='identity') +
    ylab("Catches (in tons)") + xlab('Year') +  theme_bw() +
    theme(legend.position = c(0.25,0.75), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm'))
catch.plot
```

## Biomass
Overall
``` {r}
# plotting the biomass by year
biomass.plot <- 
    ggplot(filter(fit$res.by.year, area=='area1'), 
           aes(year,total.biomass/1000, fill=stock)) +
    geom_bar(stat='identity') +
    ylab("Total biomass (in tons)") + xlab('Year') +  theme_bw() +
    theme(legend.position = c(0.25,0.75), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm')) + coord_cartesian(ylim=c(0,1e+06))
biomass.plot
```

Harvest Per Year
``` {r}
# plotting the harvest per year
harv.plot <- 
    ggplot(filter(fit$res.by.year, area=='area1'),
           aes(year,harv.biomass/1000, fill=stock)) +
    geom_bar(stat='identity') +
    ylab("Harvestable biomass (in tons)") + xlab('Year') +  theme_bw() +
    theme(legend.position = c(0.25,0.75), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm')) + coord_cartesian(ylim=c(0,1e+06))
harv.plot
```

SSB Harvest
``` {r}
# plot sustainable harvest biomass per year
ssb.plot <- 
    ggplot(filter(fit$res.by.year, area=='area1'),
           aes(year,ssb/1000, fill=stock)) +
    geom_bar(stat='identity') +
    ylab("SSB (in tons)") + xlab('Year') +  theme_bw() +
    theme(legend.position = c(0.4, 0.8), legend.title = element_blank(),
          plot.margin = unit(c(0,0,0,0),'cm')) + coord_cartesian(ylim=c(0, 2e+05))
ssb.plot
```


